Sketch Recognition and Understanding

### 2009-09-26 trunk/draft/System.tex

 	\begin{itemize}
\item \emph{Size Ratio} Ratio between width to height of the symbol.
		\item \emp{Log of size Ratio} Log of the ratio between width and height of symbol.
	\item \emph{Ink density} Compute the density of points inside its bounding box\cite{GeometryAndDomain102}.   
 	\item \emph{Convex Hull Area} Area of convex hull with respect to area of bounding box of symbol.

@@

	\item \emph{Mean Time difference} The mean of the time difference between each two successive points in the symbol. %Different strokes are appended to construct a single path.
	%\item [Ra]		
			\item \emp{Log of Area} Log of area of the symbol.
	\item \emph{Diff Area} Absolute difference of the area of bounding box and area of symbol.

@@

\begin{figure}
	\centering
		\includegraphics{afterDefense/svm6.jpg.eps}
	\caption{non Linearly problem }
	\label{fig:svm6}
\end{figure}

@@

	\includegraphics[scale=0.5]{afterDefense/clockstroke1.eps}
  &   &    
\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
The circle is   a = 103.05715108084719 ,b = 103.06851874747797 , Center( 283.03365107691775,  181.05035287667172 )   with Error =  1.9471676673301757 , Percent =1.0695193086531243
eff  = 0.27463462099275116

@@

Stroke 2 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} &
 	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps} \\ \hline
  & Possible Dominate point Extraction for details see Section\ref{sec:Preprocessing} &   	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps}  & 1. compute the $P_{pd}$  & 
    \\ \hline

>>>>

 	\begin{itemize}
\item \emph{Size Ratio} Ratio between width to height of the symbol.
		\item \emph{Log of size Ratio} Log of the ratio between width and height of symbol.
	\item \emph{Ink density} Compute the density of points inside its bounding box\cite{GeometryAndDomain102}.   
 	\item \emph{Convex Hull Area} Area of convex hull with respect to area of bounding box of symbol.

@@

	\item \emph{Mean Time difference} The mean of the time difference between each two successive points in the symbol. %Different strokes are appended to construct a single path.
	%\item [Ra]		
			\item \emph{Log of Area} Log of area of the symbol.
	\item \emph{Diff Area} Absolute difference of the area of bounding box and area of symbol.

@@

\begin{figure}
	\centering
		\includegraphics{afterDefense/svm6.jpg.eps}
	\caption{Example of an non Linearly SVM Problem }
	\label{fig:svm6}
\end{figure}

@@

	\includegraphics[scale=0.5]{afterDefense/clockstroke1.eps}
  &   &    \includegraphics[scale=0.5]{afterDefense/stroke1withpdp.jpg.eps}
\\ \hline 
Segmentation & Segmentation of Ellipse & $P_{dp}$   &  Ellipse fitting  & 
The circle is   a = 103.05715108084719 ,b = 103.06851874747797 , Center( 283.03365107691775,  181.05035287667172 )   with Error =  1.9471676673301757 , Percent =1.0695193086531243
eff  = 0.27463462099275116

@@

Stroke 2 & Extracting point and computing boundary data & -- &  see Section \ref{sec:Preprocessing} &
 	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps} \\ \hline
  & Possible Dominate point Extraction for details see Section\ref{sec:Preprocessing} &   	\includegraphics[scale=0.5]{afterDefense/clockstroke2.jpg.eps}  & 1. compute the $P_{pd}$  &

  \includegraphics[scale=0.5]{afterDefense/stroke2WithPdp.jpg.eps}
    \\ \hline
